---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Clustering Datasets

An R-repackaging of datasets useful for evaluating clustering methods.  The source for most is http://cs.joensuu.fi/sipu/datasets 

I would love to include additional clustering datasets, if folks would like to provide them or make a PR.

```{r child = 'vignettes/clusteringdatasets.Rmd'}
```

## Sklearn Toy Datasets

The Python `sklearn.datasets` package includes functions for creating toy datasets.  I've ported a few of them. 

### Make Blobs

```{r makeblobs,echo=T}
library(clusteringdatasets)
blobs <- make_blobs(centers=matrix(c(-7, -5, 6, -7, 3, 6), ncol=2))
plot(blobs$samples, col=rainbow(3)[blobs$labels], xlim=c(-10, 10), ylim=c(-10, 10))
```

### Make Moons

```{r makemoons,echo=T}
moons <- make_moons(noise=0.04)
plot(moons$samples, col=rainbow(2)[moons$labels])
```